% Standard LaTeX Resume Template
% Based on awesome-cv but simplified for pdflatex compatibility

\documentclass[11pt,a4paper]{article}

% Essential packages
\usepackage[margin=0.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tabularx}

% List formatting
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.2em}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]

% Helper commands
\newcommand{\resumeItem}[2]{\item \textbf{#1:} #2}
\newcommand{\resumeBullet}[1]{\item #1}

% Color definitions
\definecolor{accentcolor}{HTML}{000066}

\begin{document}

% Header
\begin{center}
{\LARGE \textbf{Anurag Tiwari}} \\
Bengaluru, India \,|\, \href{mailto:anuragmtiwari@outlook.com}{anuragmtiwari@outlook.com} \,|\, +91-7678537602 \,|\, 
\href{https://github.com/iotbyanurag}{github.com/iotbyanurag} \,|\, 
\href{https://linkedin.com/in/anurag0079090}{linkedin.com/in/anurag0079090}
\end{center}

% Summary
\section*{Summary}
Principle-level Embedded Software Engineer (10+ yrs) specializing in \textbf{Yocto BSPs}, \textbf{Xilinx Zynq (PS)}, 
\textbf{Embedded Linux}, and \textbf{device drivers} (incl. \textbf{MIPI CSI-2} camera). Built and containerized \textbf{Cloud RAN} 
apps (Docker/Kubernetes), automated validation (\textbf{Robot Framework}, Jenkins), and delivered 
production-grade firmware/services with strong DT\&E discipline. Recent work at \textbf{CommScope} spans 
RAN managers (DM/AM/PFM), microservices (gRPC), and Kafka-backed logging—\textbf{improving test coverage 
and release velocity}.

% Skills
\section*{Skills}
\textbf{Low-Level \& Drivers:} Linux device drivers, MIPI CSI-2 camera pipeline, V4L2, I2C/SPI/UART, DMA, IRQs, GPIO, pinmux \\
\textbf{Kernel \& BSP/Yocto:} Yocto (distro layers, recipes, images), U-Boot, initramfs, systemd, kernel config/patches \\
\textbf{Board Bring-Up \& Debug:} Xilinx Zynq(PS), boot flow, DDR, clocks, PMIC, JTAG, logic analyzer, oscilloscope \\
\textbf{RAN \& Cloud-Native:} C/C++, gRPC, Kafka, Docker, Kubernetes, microservices, CI/CD, observability \\
\textbf{Tooling \& Automation:} Robot Framework, Jenkins, Git, JIRA, DOORS, Enterprise Architect \\
\textbf{Languages:} C, C++, Embedded C, Python, Shell; Web (React, Node.js) where relevant

% Experience
\section*{Experience}
\textbf{Research \& Development Engineer II} \hfill Jan 2022 -- Present \\
CommScope, Bengaluru
\begin{itemize}
  \resumeBullet{Owned Yocto BSP and image customization for Cloud RAN appliances; streamlined layer hygiene and CI, reducing image build time by \textbf{22\%} and field rollouts by \textbf{$\sim$1 day/release}.}
  \resumeBullet{Implemented PS-side drivers and user-space control paths (I2C/SPI, DMA, IRQ) for radio subsystems; cut bring-up defects by \textbf{30\%}.}
  \resumeBullet{Developed MIPI CSI-2 camera capture path on Embedded Linux (V4L2, media graph, sensor init, lane config); stabilized streaming with \textbf{0 dropped frames} in 30-min soak.}
  \resumeBullet{Containerized RAN managers (DM/AM/PFM) with \textbf{gRPC} interfaces; deployed on \textbf{Kubernetes}; integrated \textbf{Kafka} log streaming and probes for SLOs.}
  \resumeBullet{Established Robot Framework + Jenkins test automation across multi-node rigs, increasing regression coverage from \textbf{$\sim$45\%} to \textbf{>80\%}.}
\end{itemize}

\textbf{Software Engineer} \hfill Nov 2018 -- Jan 2022 \\
Capgemini, Gurgaon
\begin{itemize}
  \resumeBullet{Developed automotive embedded software using \textbf{AUTOSAR} architecture for instrument clusters; implemented telltale and door warning applications with Embedded C and Vector tools (CANalyzer, CANoe, DaVinci).}
  \resumeBullet{Executed comprehensive testing strategy spanning Unit, Functional, Integration, and System levels; enhanced software reliability and compliance with automotive standards.}
  \resumeBullet{Designed Smart-Grid Network Interface Card applications featuring \textbf{Over-The-Air (OTA)} updates and commissioning processes; improved field deployment efficiency by \textbf{25\%}.}
  \resumeBullet{Maintained code quality and documentation using JIRA, DOORS, and Enterprise Architect; established coding standards that reduced integration defects by \textbf{40\%}.}
\end{itemize}

\textbf{IoT Support Engineer} \hfill Jan 2018 -- Aug 2018 \\
BuffaloGrid Project Pvt Ltd, Delhi
\begin{itemize}
  \resumeBullet{Developed firmware for distributed solar-powered mobile charging hubs; implemented \textbf{FOTA updates} and Battery Management System (BMS) software for field-deployed units.}
  \resumeBullet{Created test automation scripts reducing manual QA effort by \textbf{40\%}; enhanced product testing reliability and deployment validation.}
\end{itemize}

\textbf{Embedded Software Engineer} \hfill Dec 2015 -- Dec 2017 \\
Eigen Technologies Pvt Ltd, Delhi
\begin{itemize}
  \resumeBullet{Led electronic design and firmware development for WSN-based smart streetlight and BLE-based home automation products; delivered end-to-end IoT solutions.}
  \resumeBullet{Implemented multi-protocol firmware supporting 802.15.4 protocols including Zigbee; conducted comprehensive QA testing ensuring compatibility across devices.}
  \resumeBullet{Architected and deployed IoT dashboard on AWS with real-time data visualization; integrated with 4G module gateway using AT commands for remote monitoring.}
\end{itemize}

% Selected Low-Level Systems Projects
\section*{Selected Low-Level Systems Projects}
\textbf{Yocto BSP for Custom Zynq Board} — Distro layers, U-Boot patches, kernel config, image recipes; reduced boot time via systemd unit profiling and init sequence trimming. 
\newline
\textbf{MIPI CSI-2 Camera Driver \& Pipeline} — Sensor init (I2C), CSI lane timing, V4L2 sub-dev, media controller graph; validated with long-run soak, artifact-free frames.
\newline
\textbf{PS-Side DMA/Interrupt Path} — Engineered robust DMA ring buffers and IRQ service; back-pressure handling to maintain deterministic throughput.
\newline
\textbf{RAN Microservices on K8s} — gRPC services (DM/AM/PFM), Kafka log bus, readiness/liveness probes; Helm deploys and blue/green updates.
\newline
\textbf{HW Bring-Up \& Debug} — Pinmux, clock tree, PMIC init; boundary scan + JTAG; logic analyzer traces for ISR latency verification.

% Education
\section*{Education}
B.Tech in Electrical \& Electronics, GGSIPU (2014), Score 70.5\%

\vfill
\footnotesize Updated on: \today

% ATS-KEYWORDS: Yocto, BSP, U-Boot, Embedded Linux, Linux device drivers, MIPI CSI-2, V4L2, Xilinx Zynq, PS, DMA, IRQ, I2C, SPI, GPIO, Robot Framework, Jenkins, Kafka, gRPC, Docker, Kubernetes, Cloud RAN, RTOS
\end{document}